---
title: "HW2"
author: "Jason Martinelli, G4"
date: "9/8/22"
output: word_document
---
\newpage


# Problems

# Computer exercises

```{r include=FALSE}
library(wooldridge)
library(dplyr)
```



## Question 1 

Replicate the following vector of numbers using **seq()** function and call it **v1.**

```{r, comment=NA}

v1 <- seq(from = 1,to = 17,by = 4)
v1

```

----

## Question 2 

### part I

Replicate the following matrix in R and call it A.

```{r, comment=NA}
A <- matrix(20:39,4,5, byrow = TRUE)
A

```

### part II

```{r, comment=NA}
colnames(A)<-(c('A','B','C','D','E'))
A
```

### part III

```{r, comment=NA}
B <- A[c(2,4), c("B", "D")]
B
```

### part IIII

```{r, comment=NA}
t(B)
```

### part V

```{r, comment=NA}
B.inverse <- solve(B)
B.inverse
```

### part VI

```{r, comment=NA}
B2 <- B.inverse%*%B
B2
```

### Question 3 part I

```{r, comment=NA}
df <- mtcars
head(df,10)

```

### part II

```{r, comment=NA}

library(dplyr)
df1<-df
df1 <- arrange(select(df,c("cyl","hp","wt","vs","am","gear","mpg")),cyl==4)
head(df1,5)
```

### part III

```{r, comment=NA}

df1<-round(mutate(df1,gpm=1/mpg),3)
df1

```

### part IIII

```{r, comment=NA}
str(df1)
```

### part V

```{r, comment=NA}
df1$vs<-factor(df1$vs)
df1$am<-factor(df1$am)
df1$cyl<-factor(df1$cyl)
df1$gear<-factor(df1$gear)
str(df1)
```


### Question 4 part I

```{r, comment=NA}
c<-table(alcohol$abuse)
prop.table(c)
```
The prop table shows that percentage of men that abuse alcohol, which is .0991, or about 10%.

### part II

```{r, comment=NA}
c<-table(alcohol$employ)
prop.table(c)
```

The employment rate is 89.81%, or about 90%. 

### part III


```{r, comment=NA}
c<-table(alcohol$employ, alcohol$abuse)
prop.table(c, margin = 2)
```

The employment rate of those that abuse alcohol, noted as (1,1) on the table above, is 0.87268994, or about 87.26%.

### part IIII

The employment rate of those who do not abuse alcohol, noted as (0,1) on the table above, is 0.90099458, or about 90.1%.

### part V
Based on these observations alone, it cannot be concluded whether or not alcohol causes unemployment, as there is a <3% difference in those who are and are not abusers of alcohol. 













